---
title: "Data Analysis"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
require(reshape)
require(sqldf)
require(ggplot2)
require(igraph)
require(RCurl)
```

## Initial Procedures

First of all, we load the datasets and then:
   * perform some "reshaping" (using the melt function) of the datasets
   * filter the datasets to only consider valid primary studies

```{r}
d1 <- getURL("http://rbonifacio.net/papers/delta-slr/datasets/concern.csv")
d2 <- getURL("http://rbonifacio.net/papers/delta-slr/datasets/empirical-method.csv")
concern <- read.csv(text=d1, head=T)
empiricalMethod <- read.csv(text=d2, head=T)
empiricalMethod <- melt(empiricalMethod, c("ID"))
empiricalMethod <- sqldf("select ID, variable as Method from empiricalMethod where value = 'Y'")
```

To build the bubble plot of the paper, it is necessary to join both datasets (*empiricalMethods* and *SPL concern*). 

```{r}
concernMethod <- sqldf("SELECT c.ID, c.Concern, em.Method 
                        FROM concern c, empiricalMethod em 
                        WHERE c.ID = em.ID")
```

It is also interesting to export the joined dataset and summarize the data, so that we could provide 
one more cleanup session. That is, it might be important to remove some details that are not 
necessary to our analysis. Particularly, the subclassification of variability management in the 
resulting dataset was condensed in the paper. We also summarize the datase. Note that, here we 
load a processed data-set. 

```{r}
# write.csv(concernMethod,file="/Users/rbonifacio/Documents/delta-slr/data/concern-method.csv")
d1 <- getURL("http://rbonifacio.net/papers/delta-slr/datasets/concern-method.csv")
concernMethod <- read.csv(text=d1, head=T)
concernMethod.summary <- sqldf("SELECT Concern, Method, count(*) as Count 
                                FROM concernMethod 
                                GROUP BY Concern, Method")
```

Now, we are ready to generate a bubble plot. 

```{r pressure, echo=FALSE}
p <- ggplot(concernMethod.summary, aes(Concern,Method,size=Count, label=Count))
p <- p+geom_point(colour="lightgray") + scale_size_area(max_size=20) + geom_text(size=5)
p + ylab("") + xlab("") + theme_bw()
```

### Social network analysis of the primary studies 

In this section we build several graphs for reasoning 
about the relationships between authors of 
the primary studies. 

We first generate a CSV file 
having the id of the primary study and the names of each 
author of the paper (separated by a semicolon)
We implemented a Python script that takes a file 
with this structure and exports two new files: one with 
a list of authors (the list of vertices of the 
graph) and one with the relationships (the edges of the 
graph) between the authors of the papers. 

Actually, this second 
file has three columns: author one, author two, 
and weight (the number of times the two authors 
co-author together). With this two files, we 
use the *igraph* R package to build the 
graph and reason about some of its properties. 

```{r}
d1 <- getURL("http://rbonifacio.net/papers/delta-slr/datasets/delta-vertices.csv")
d2 <- getURL("http://rbonifacio.net/papers/delta-slr/datasets/delta-edges.csv")
vs <- read.csv(text=d1,head=T)
es <- read.csv(text=d2,head=T)
mg <- graph_from_data_frame(d=es, vertices=vs, directed=F)
mg2 <- delete.edges(mg,E(mg)[weight == 1])
mg3 <- delete_vertices(mg2,V(mg2)[Papers == 1])

par(mfrow = c(1,2),
    oma = c(5,4,0,0) + 0.1,
    mar = c(0,0,1,1) + 0.1)
plot(mg, vertex.label=NA, vertex.size=V(mg)$Papers)
plot(mg3, vertex.label=NA, vertex.size=V(mg3)$Papers)
# d1 <- getURL("http://rbonifacio.net/papers/delta-slr/datasets/primary-studies")
# ps <- read.csv(text=d1,head=T)
# Year = factor(ps$Year)
# plot(table(Year),type="o")
```


### AOP + SPLines author networks

We also build similar graphs to AOP + SPLines and FOP. As an example: 

```{r}
vs <- read.csv("http://rbonifacio.net/papers/delta-slr/datasets/aop-spl-vertices.csv", head=T)
es <- read.csv("http://rbonifacio.net/papers/delta-slr/datasets/aop-spl-edges.csv",head=T)
mg <- graph_from_data_frame(d=es, vertices=vs, directed=F)
mg2 <- delete.edges(mg,E(mg)[weight == 1])
mg3 <- delete_vertices(mg2,V(mg2)[Papers == 1])
par(mfrow = c(1,2),
    oma = c(5,4,0,0) + 0.1,
    mar = c(0,0,1,1) + 0.1)
plot(mg, vertex.label=NA, vertex.size=V(mg)$Papers)
plot(mg3, vertex.label=NA, vertex.size=V(mg3)$Papers)
```

```{r}
library(ggplot2)
ps <- read.csv("Documents/delta-slr/data/primary-studies.csv", head=T)
mds <- as.data.frame(ps$Category1)
ggplot(mdf, aes(x=reorder(Var1, +Freq), y=Freq)) + geom_bar(stat="identity",fill="#FFCC99",colour="black") + xlab("") + ylab("")
```